\section{Group Members Contribution}
% For each group member, describe in detail the contribution to the project.

\begin{description}
	\item[Heldal Julie Marie] worked on homework report, in particular on the mockup for the homepage, PLL text file for homepage and sequence diagram BLL section.
	\item[Hermansen Kathrine] worked on the homework report by making mockups for the login, registration and front office page, PLL text files (login and registration, front office) and the Class Diagram BLL section.
	\item[Kosiakov Arina] worked on the homework report, in particular on the mockups for booking and personal page, PLL text files (Booking page, Personal page, Main Fnctionalities), BLL section some contributions to the coding Log part
	\item[Lotta Tommaso] worked on the coding part related to Booking (servlet, resource, dao and rest), Payment, Log and other general files needed for the coding part in java. Worked on the database sql code. Wrote the rest api summary and details.
	\item[Manuilova Nadezhda] worked on the homework report: Objectives of the system, Main functionalities, Data logic layer (ER-Schema).
	\item[Mohammadi Mohammadreza] Room Entity servlet, resource - General setting of POM, web.xml - User Rest API - Rest API report - REST API general setting - REST API message class - Search of not payed booking
	\item[Roennestad Andreas] worked on the implementation of the Customer-entity related part of the backend providing functionality for registering, updating, deleting Customers etc. This included the Customer servlet, registration jsp, and the related database operation classes.
	\item[Vignaga Marco] User, Customer and Payments related jsp, dao and servlets.
	\item[Zuccolo Giada] Mockups and report.
\end{description}
% For each group member, describe in detail the contribution to the project.

