\section{Main Functionalities}
This web application will be mainly used to allow registered users to book a room in the hotel (with different booking options based on the logged account) and to enroll for the events that are taken in the hotel.\\ 
The web interface allows also to modify user's data and add new users. It will also be possible for the hotel manager, and it's employees, to manage orders received from customers.\\

The website is divided in 5 main areas:
\begin{itemize}
    \item  Public area: this area corresponds to the homepage of the web application and it is accessible to both registered and unregistered users. In particular, in this area is possible to:
    \begin{itemize}
        \item find basic information about the hotel and activities;
        \item find contact information (email, telephone, address);
        \item find available dates for booking.     
    \end{itemize}

    \item Customer area:
    
    Booking:
    \begin{itemize}
    
        \item show available rooms for required dates;
        \item show details of the room;
        \item send confirmation emails;
        \item show payment methods;
        \item show past bookings;
    \end{itemize}

    Profile:
    \begin{itemize}
        \item check personal information;
        \item check bookings;
        \item change settings;
        \item help desk;
        \item choose payment methods.
    \end{itemize}
    \item Login area:
    \begin{itemize}
        \item registration for customers;
        \item login for customers;
        \item login for users.
    \end{itemize}
    \item Administration area: the administration area is accessible only to users with the role “Hotel Manager”. It contains functionalities to operate over the users in the system. In particular, in this area is possible to:
    \begin{itemize}
        \item search users via username, email;
        \item retrieve information on a specific user;
        \item check payments;
        \item modify the user record by changing their first name, last name and role;
        \item view all the information about the bookings; 
        \item add new users;
        \item perform all the actions of the "Front Office" user;
    \end{itemize}
        \item User area: the user area is accessible to users with the role "Front Office". It contains a series of functionalities in order to interact with customers. Some of this functionalities are the following: 
    \begin{itemize}
        \item accept payments;
        \item retrieve inforcurrent bookings;
        \item check the available rooms;
        \item add, delete,update a booking;        
    \end{itemize}
\end{itemize}



