\subsection{REST Error Codes}

%If needed, add few lines of text, describing the error codes table
The following list contains the different possible errors which can occure by using the application. In particular, application specific errors have the application error which follows a progressive numeration starting from -100. 
METHOD NOT ALLOWED errors are identified with the error code -500.
Internal errors, which correspond to crashes, servlet exceptions, or problems with the input/output streams are identified with the Error Code -999.

\begin{longtable}{|p{.15\columnwidth}|p{.2\columnwidth} |p{.6\columnwidth}|} 
\hline
\textbf{Error Code} & \textbf{HTTP Status Code} & \textbf{Description} \\\hline
-100 & BAD\_REQUEST            & Wrong Person id format. \\ \hline
-101 & NOT\_FOUND              & The user is looking for a room which is not present. \\ \hline
-102 & BAD\_REQUEST            & The user tried to register without specifying all the details. Used also with forms that need to be fully filled. \\ \hline
-103 & BAD\_REQUEST            & The user tried to login without specifying the Email. \\ \hline
-104 & BAD\_REQUEST            & The user tried to login without specifying the password. \\ \hline
-105 & BAD\_REQUEST            & User submitted wrong credentials in the login form. \\ \hline
-106 & NOT\_FOUND              & User to be deleted not found. \\ \hline
-107 & BAD\_REQUEST            & Different passwords when repeating the password in the registration phase. \\ \hline
-108 & CONFLICT                & Mail already used for another registration. \\ \hline
-109 & BAD\_REQUEST            & Unrecognized role. \\ \hline
-110 & CONFLICT                & User is already present. \\ \hline
-111 & BAD\_REQUEST            & Invalid document number. \\ \hline
-112 & BAD\_REQUEST            & Wrong rest request format. \\ \hline
-113 & NOT\_FOUND              & Costumer not found. \\ \hline
-114 & CONFLICT                & Person ID requested and Person ID provided do not match. \\ \hline
-115 & NOT\_FOUND              & User not found. \\ \hline
-116 & BAD\_REQUEST            & Person ID is missing. \\ \hline
-117 & NOT\_FOUND              & Booking not found. \\ \hline
-118 & BAD\_REQUEST            & Date is missing. \\ \hline
-119 & BAD\_REQUEST            & The input json is in the wrong format. \\ \hline
-200 & BAD\_REQUEST            & Operation unknown. \\ \hline
-500 & METHOD\_NOT\_ALLOWED    & The method is not allowed. \\ \hline
-999 & INTERNAL\_SERVER\_ERROR & There was an internal error that the server was not able to manage. \\ \hline

\caption{Describe in this table your REST API}
\label{tab:termGlossary}
\end{longtable}